Simulation and visualization framework for decision making of climate mitigation \vspace{4pt} and adaptation strategies in new and existing urban development

### 2021-01-30 manuscript_wesbrook-bigmacc_BS2021.tex

@@

MACCs were drawn as another form of visualising decision making. Figure \ref{fig:MACC_budget} is drawn under the assumption that planners are expecting a worst-case climate change scenario by the end of the century, have set a budget of an additional \$11,000,000 that could be invested across the development on mitigation and adaptation strategies. The drawn MACC then presents every possible combination under the development and climate change trajectory that falls below the budget. Another MACC was drawn, Figure \ref{fig:MACC_threshold} assuming an emissions reduction threshold of 80\% by 2050 under the best-case climate scenario.

>>>>

\begin{figure}[hbpt]
    \centering
    \includegraphics[scale=1.0]{figures/general_results.eps}
    \caption{General results from the iterations.}
    \label{fig:joint_plot}
\end{figure}

@@

\begin{figure*}[hbpt]
    \centering
    \includegraphics[scale=0.8]{figures/optimal_plots.eps}
    \caption{Plotting marginal abatement cost and the adaptation metric to serve as a canvas for pathway planning.}
    \label{fig:joint_plot}
\end{figure*}

MACCs were drawn as another form of visualising decision making. Figure \ref{fig:MACC_budget} is drawn under the assumption that planners are expecting a worst-case climate change scenario by the end of the century and have set a budget of an additional \$11,000,000 that could be invested across the development on mitigation and adaptation strategies. The drawn MACC then presents every possible combination under the development and climate change trajectory that falls below the budget. Another MACC was drawn, Figure \ref{fig:MACC_threshold} assuming an emissions reduction threshold of 80\% by 2050 under the best-case climate scenario. A third MACC was generated under the assumption that planners would be interested in decarbonizing without abandoning the district heating system, the bulk of the emissions.

To illustrate the construction of a more authentic MACC, we began with the combination of strategies that produced the best degree of adaptability under the worst-case climate change scenario at the end of the century, where the most hours outside of the comfort threshold were reduced. This strategy-set could have been any of those in Table \ref{tab:worst_case_adapt}.
